Impacts of Month, Grocery Vendor, Presale Prices, and Historical Pricing on Discounted Egg Dozen Prices

### 2024-12-04 paper/paper.qmd
added sketches + deleted unused files

@@

## Observational Data {#sec-obs-data}

@@

>>>>

@fig-monthsales shows the number of sales provided on egg dozens across the months, with the least number of sales occuring in July and most in November.

@@

## Observational Data and Sampling {#sec-obs-data}

@@

There are also potential weaknesses introduced by each level of sampling for this analysis. First, when Project Hammer scrapes the grocer websites, there may be items that were not tracked within this dataset. Especially before July, when information on a greater variety of products started being collected, there may be many missed entries of discounts on eggs. This introduces a potential sampling bias that may impact the accuracy of the model's results. Further, due to the selection of these 8 specific vendors in Canada, there may pricing patterns at other grocery chains that are unobservable from this dataset. For example, how would family-run grocery stores compare to these large chains? Are there similarities in pricing patterns across the months, or would they exhibit completely different behaviour?
